---
title: "Memory Request Visualizer"
subtitle: "How request_memory Changes Job Throughput"
output:
  html_document:
    toc: false
    theme: flatly
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(purrr)
library(plotly)
```

Use the checkboxes in the table to pick `request_memory` tiers — for the
1,000-job clusters, the 10,000-job clusters, or both — and the plots below
update to show only what you've checked. All data is real: HTCondor clusters
of 1,000 and 10,000 `mc_pi.py` jobs, each submitted 3 times at each of 8
memory requests from 500 MB to 64 GB, with everything else unchanged across
runs.

```{r load-data}
tiers  <- c("500MB", "1GB", "2GB", "4GB", "8GB", "16GB", "32GB", "64GB")
mb_map <- c("500MB" = 500, "1GB" = 1024, "2GB" = 2048, "4GB" = 4096,
            "8GB" = 8192, "16GB" = 16384, "32GB" = 32768, "64GB" = 65536)
scales       <- c(1000, 10000)
scale_labels <- c("1,000 jobs", "10,000 jobs")

read_tier <- function(scale, tier, tier_idx) {
  base <- file.path("memory", paste0("mc_runs_", scale, "_mem_", tier))
  run_dirs <- list.dirs(base, recursive = FALSE)
  run_dirs <- run_dirs[grepl("^run_", basename(run_dirs))]
  purrr::map_dfr(run_dirs, function(rd) {
    f <- file.path(rd, "results.csv")
    if (!file.exists(f)) return(NULL)
    df <- read.csv(f)
    df$run <- basename(rd)
    df
  }) %>%
    mutate(mb = mb_map[[tier]], tier = tier, tier_idx = tier_idx,
           scale = scale, scale_idx = match(scale, scales) - 1)
}

long_df <- purrr::map_dfr(scales, function(s) {
  purrr::imap_dfr(tiers, ~ read_tier(s, .x, .y - 1))
}) %>%
  group_by(scale, tier) %>%
  mutate(run_num = dense_rank(run)) %>%
  group_by(scale, tier, run) %>%
  arrange(turnaround_s, .by_group = TRUE) %>%
  mutate(cum_jobs = row_number()) %>%
  ungroup()

summary_df <- long_df %>%
  group_by(scale, scale_idx, tier, tier_idx, mb) %>%
  summarise(.groups = "drop") %>%
  left_join(
    long_df %>%
      group_by(scale, tier, run) %>%
      summarise(total_time_s = max(turnaround_s, na.rm = TRUE), .groups = "drop") %>%
      group_by(scale, tier) %>%
      summarise(median_total_time_s = median(total_time_s), .groups = "drop"),
    by = c("scale", "tier")
  ) %>%
  arrange(scale, mb)

n_tiers  <- length(tiers)
n_runs   <- 3
n_scales <- length(scales)

# Categorical palette, one fixed color per tier (validated, light mode).
tier_colors <- c("#2a78d6", "#eb6834", "#1baf7a", "#eda100",
                 "#e87ba4", "#008300", "#4a3aa7", "#e34948")
tier_fills <- vapply(tier_colors, function(hex) {
  v <- grDevices::col2rgb(hex)
  sprintf("rgba(%d,%d,%d,0.15)", v[1], v[2], v[3])
}, character(1))

# Thin the 10,000-point cumulative curves so the self-contained HTML stays
# small; the step curve is visually identical at ~400 points.
thin_curve <- function(d, max_pts = 400) {
  n <- nrow(d)
  if (n <= max_pts) return(d)
  d[unique(c(round(seq(1, n, length.out = max_pts)), n)), ]
}

# Heading annotation placed above a subplot panel (paper coordinates).
panel_heading <- function(label, x, y) {
  list(text = paste0("<b>", label, "</b>"), x = x, y = y,
       xref = "paper", yref = "paper",
       xanchor = "center", yanchor = "bottom",
       showarrow = FALSE, font = list(size = 15))
}

box_stats <- function(y) {
  q1 <- unname(quantile(y, 0.25, na.rm = TRUE))
  q3 <- unname(quantile(y, 0.75, na.rm = TRUE))
  iqr <- q3 - q1
  list(q1 = q1, med = median(y, na.rm = TRUE), q3 = q3,
       lf = min(y[y >= q1 - 1.5 * iqr], na.rm = TRUE),
       uf = max(y[y <= q3 + 1.5 * iqr], na.rm = TRUE))
}
```

## Pick memory requests

Each row is one `request_memory` value; its color swatch matches that tier's
color in every plot. Check a box to show that tier's runs at that cluster
size.

<style>
#tier-table { border-collapse: collapse; margin: 1em 0 1.6em; }
#tier-table th, #tier-table td {
  border: 1px solid #e1e0d9; padding: 0.45em 0.9em; text-align: center;
}
#tier-table th { background: #f9f9f7; font-weight: 600; color: #0b0b0b; }
#tier-table td.tier-name { text-align: left; font-weight: 600; }
#tier-table .swatch {
  display: inline-block; width: 11px; height: 11px; border-radius: 3px;
  margin-right: 0.5em; vertical-align: baseline;
  box-shadow: 0 0 0 1px rgba(11,11,11,0.10);
}
#tier-table input[type="checkbox"] {
  width: 16px; height: 16px; accent-color: #2a78d6; cursor: pointer;
}
</style>

```{r tier-table, results='asis'}
cat('<table id="tier-table">\n<thead>\n',
    '<tr><th>request_memory</th>',
    '<th>1,000 jobs</th><th>10,000 jobs</th></tr>\n',
    '</thead>\n<tbody>\n', sep = "")

for (ti in seq_len(n_tiers) - 1) {
  checked <- if (ti == 0) ' checked' else ''
  cat(sprintf(paste0(
    '<tr><td class="tier-name"><span class="swatch" style="background:%s"></span>%s</td>',
    '<td><input type="checkbox" class="tier-cb" data-scale="0" data-tier="%d"%s></td>',
    '<td><input type="checkbox" class="tier-cb" data-scale="1" data-tier="%d"%s></td></tr>\n'),
    tier_colors[ti + 1], tiers[ti + 1],
    ti, checked, ti, checked))
}
cat('</tbody>\n</table>\n')
```

<script>
(function() {
  var N_TIERS = 8, N_RUNS = 3, N_SCALES = 2;
  var TIER_COLORS = ["#2a78d6","#eb6834","#1baf7a","#eda100",
                     "#e87ba4","#008300","#4a3aa7","#e34948"];

  function plotReady(id) {
    var el = document.getElementById(id);
    return (el && el.data && window.Plotly) ? el : null;
  }

  function checkedMatrix() {
    var m = [];
    for (var s = 0; s < N_SCALES; s++) {
      m.push(new Array(N_TIERS).fill(false));
    }
    document.querySelectorAll(".tier-cb").forEach(function(cb) {
      m[+cb.dataset.scale][+cb.dataset.tier] = cb.checked;
    });
    return m;
  }

  function apply() {
    var m = checkedMatrix();

    // Overview: trace 0 = 1,000-job panel, trace 1 = 10,000-job panel.
    // Checked tiers get their tier color and a larger marker.
    var overview = plotReady("overview-plot");
    if (overview) {
      for (var s = 0; s < N_SCALES; s++) {
        var sizes = [], colors = [];
        for (var t = 0; t < N_TIERS; t++) {
          sizes.push(m[s][t] ? 14 : 8);
          colors.push(m[s][t] ? TIER_COLORS[t] : "#c3c2b7");
        }
        Plotly.restyle(overview, { "marker.size": [sizes],
                                   "marker.color": [colors] }, [s]);
      }
    }

    // Throughput: traces ordered scale-major — scale 0 tiers 0..7 x 3 runs,
    // then scale 1. Index = s*24 + t*3 + r.
    var throughput = plotReady("throughput-plot");
    if (throughput) {
      var visT = [];
      for (var s = 0; s < N_SCALES; s++)
        for (var t = 0; t < N_TIERS; t++)
          for (var r = 0; r < N_RUNS; r++)
            visT.push(m[s][t]);
      Plotly.restyle(throughput, { visible: visT });
    }

    // Latency: 2 panels (1k, 10k), each tier contributing 2 boxes
    // (turnaround, queue wait). Index = s*16 + t*2 + metric.
    var latency = plotReady("latency-plot");
    if (latency) {
      var visL = [];
      for (var s = 0; s < N_SCALES; s++)
        for (var t = 0; t < N_TIERS; t++)
          for (var k = 0; k < 2; k++) visL.push(m[s][t]);
      Plotly.restyle(latency, { visible: visL });
    }
  }

  function init() {
    document.querySelectorAll(".tier-cb").forEach(function(cb) {
      cb.addEventListener("change", apply);
    });

    // Plots render after DOMContentLoaded; retry until they exist, then sync
    // to the checkboxes' current state (browsers can restore it on reload).
    var tries = 0;
    var timer = setInterval(function() {
      tries++;
      if (plotReady("overview-plot") && plotReady("throughput-plot") &&
          plotReady("latency-plot")) {
        clearInterval(timer);
        apply();
      } else if (tries > 100) {
        clearInterval(timer);
      }
    }, 100);
  }

  if (document.readyState === "loading") {
    document.addEventListener("DOMContentLoaded", init);
  } else {
    init();
  }
})();
</script>


## Throughput for the checked tiers

Cumulative jobs completed vs. time since `condor_submit` — 3 runs per checked
tier, colored by tier. Top panel: 1,000-job clusters; bottom: 10,000-job
clusters.

```{r throughput-plot, fig.height=7}
throughput_panel <- function(s_idx) {
  p <- plot_ly()
  for (ti in seq_len(n_tiers) - 1) {
    for (r in seq_len(n_runs)) {
      d <- long_df %>%
        filter(scale_idx == s_idx, tier_idx == ti, run_num == r) %>%
        thin_curve()
      p <- add_trace(
        p, x = d$turnaround_s, y = d$cum_jobs,
        type = "scatter", mode = "lines",
        line = list(width = 2, color = tier_colors[ti + 1]),
        visible = (ti == 0), showlegend = FALSE,
        hoverinfo = "text",
        text = paste0(d$tier, " (", scale_labels[s_idx + 1], ") run ", r,
                      ": ", round(d$turnaround_s, 1), "s \u2014 ",
                      d$cum_jobs, " jobs done")
      )
    }
  }
  p %>% layout(
    xaxis = list(title = "Time since condor_submit (s)"),
    yaxis = list(title = "Jobs completed",
                 range = c(0, scales[s_idx + 1]))
  )
}

p <- subplot(throughput_panel(0), throughput_panel(1), nrows = 2,
             titleX = TRUE, titleY = TRUE, margin = 0.13) %>%
  layout(margin = list(t = 30),
         annotations = list(
           panel_heading(scale_labels[1], x = 0.5, y = 1.0),
           panel_heading(scale_labels[2], x = 0.5, y = 0.435)))
p$elementId <- "throughput-plot"
p
```

## Per-job latency for the checked tiers

Turnaround (submit &rarr; termination, filled box) and queue wait (submit
&rarr; first execution, hollow box), side by side for each checked
`request_memory`, pooled across the 3 runs. Top panel: 1,000-job clusters;
bottom: 10,000-job clusters.

```{r latency-plot, fig.height=7}
latency_panel <- function(s_idx) {
  p <- plot_ly()
  for (ti in seq_len(n_tiers) - 1) {
    for (metric in c("turnaround_s", "queue_wait_s")) {
      is_turn <- metric == "turnaround_s"
      y <- long_df %>%
        filter(scale_idx == s_idx, tier_idx == ti) %>%
        pull(!!rlang::sym(metric))
      s <- box_stats(y)
      p <- add_trace(
        p, x = tiers[ti + 1], type = "box",
        q1 = list(s$q1), median = list(s$med), q3 = list(s$q3),
        lowerfence = list(s$lf), upperfence = list(s$uf),
        name = paste0(tiers[ti + 1], " ",
                      if (is_turn) "turnaround" else "queue wait"),
        offsetgroup = metric,
        visible = (ti == 0), showlegend = FALSE,
        fillcolor = if (is_turn) tier_fills[ti + 1] else "rgba(0,0,0,0)",
        line = list(color = tier_colors[ti + 1])
      )
    }
  }
  p %>% layout(
    xaxis = list(title = "", categoryorder = "array",
                 categoryarray = tiers),
    yaxis = list(title = "Per-job latency (s)")
  )
}

lat <- subplot(latency_panel(0), latency_panel(1),
               nrows = 2, titleY = TRUE, margin = 0.13) %>%
  layout(boxmode = "group", margin = list(t = 30),
         annotations = list(
           panel_heading(scale_labels[1], x = 0.5, y = 1.0),
           panel_heading(scale_labels[2], x = 0.5, y = 0.435)))
lat$elementId <- "latency-plot"
lat
```

## Where the checked tiers sit in the overall trend

Every tier's median total completion time, one panel per cluster size —
checked tiers light up in their tier color.

```{r overview-plot, fig.height=4}
overview_panel <- function(s_idx) {
  d <- summary_df %>% filter(scale_idx == s_idx) %>% arrange(mb)
  init_sizes  <- c(14, rep(8, n_tiers - 1))
  init_colors <- c(tier_colors[1], rep("#c3c2b7", n_tiers - 1))
  plot_ly() %>%
    add_trace(
      x = d$mb, y = d$median_total_time_s,
      type = "scatter", mode = "lines+markers",
      line = list(color = "#c3c2b7", width = 2),
      marker = list(color = init_colors, size = init_sizes,
                    line = list(color = "#fcfcfb", width = 2)),
      hoverinfo = "text",
      text = paste0(d$tier, " (", scale_labels[s_idx + 1], "): ",
                    round(d$median_total_time_s), "s median total time"),
      showlegend = FALSE
    ) %>%
    layout(
      xaxis = list(title = "request_memory", type = "log",
                   tickvals = unname(mb_map), ticktext = names(mb_map)),
      yaxis = list(title = "Median total time (s)")
    )
}

ov <- subplot(overview_panel(0), overview_panel(1), nrows = 1,
              titleX = TRUE, titleY = TRUE, margin = 0.07) %>%
  layout(margin = list(t = 30),
         annotations = list(
           panel_heading(scale_labels[1], x = 0.2325, y = 1.0),
           panel_heading(scale_labels[2], x = 0.7675, y = 1.0)))
ov$elementId <- "overview-plot"
ov
```
