---
title: "Memory Request Simulator"
author: "Snikitha Siddavatam"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
subtitle: "How request_memory Changes Job Throughput"
output:
  html_document:
    toc: false
    theme: flatly
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(purrr)
library(plotly)
```

Drag the slider to pick a `request_memory` value and watch how job throughput
for that memory tier compares to the rest. All data below is real: 1,000
HTCondor jobs (S = 10,000 samples each), submitted 3 times at each of 8 memory
requests from 500 MB to 64 GB, with `mc_pi.py` otherwise unchanged across runs.

```{r load-data}
tiers  <- c("500MB", "1GB", "2GB", "4GB", "8GB", "16GB", "32GB", "64GB")
mb_map <- c("500MB" = 500, "1GB" = 1024, "2GB" = 2048, "4GB" = 4096,
            "8GB" = 8192, "16GB" = 16384, "32GB" = 32768, "64GB" = 65536)

read_tier <- function(tier, tier_idx) {
  base <- file.path("memory", paste0("mc_runs_1000_mem_", tier))
  run_dirs <- list.dirs(base, recursive = FALSE)
  run_dirs <- run_dirs[grepl("^run_", basename(run_dirs))]
  purrr::map_dfr(run_dirs, function(rd) {
    f <- file.path(rd, "results.csv")
    if (!file.exists(f)) return(NULL)
    df <- read.csv(f)
    df$run <- basename(rd)
    df
  }) %>%
    mutate(mb = mb_map[[tier]], tier = tier, tier_idx = tier_idx)
}

long_df <- purrr::imap_dfr(tiers, ~ read_tier(.x, .y - 1)) %>%
  group_by(tier) %>%
  mutate(run_num = dense_rank(run)) %>%
  group_by(tier, run) %>%
  arrange(turnaround_s, .by_group = TRUE) %>%
  mutate(cum_jobs = row_number()) %>%
  ungroup()

summary_df <- long_df %>%
  group_by(tier, tier_idx, mb) %>%
  summarise(
    median_turnaround_s  = median(turnaround_s, na.rm = TRUE),
    p90_turnaround_s     = quantile(turnaround_s, 0.9, na.rm = TRUE),
    median_queue_wait_s  = median(queue_wait_s, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    long_df %>%
      group_by(tier, run) %>%
      summarise(total_time_s = max(turnaround_s, na.rm = TRUE), .groups = "drop") %>%
      group_by(tier) %>%
      summarise(median_total_time_s = median(total_time_s), .groups = "drop"),
    by = "tier"
  ) %>%
  arrange(mb)

n_tiers <- length(tiers)
n_runs  <- 3
run_colors <- c("#9ec5f4", "#3987e5", "#0d366b")
```

## Pick a memory request

<style>
#tier-slider-wrap { max-width: 720px; margin: 1.2em 0 1.6em; }
#tier-slider-wrap .tier-readout {
  font-size: 1.15em; font-weight: 600; color: #0b0b0b;
  margin-bottom: 0.4em;
}
#tier-slider-wrap .tier-readout span { color: #2a78d6; }
#tier-range {
  width: 100%; -webkit-appearance: none; appearance: none;
  height: 4px; border-radius: 2px; background: #e1e0d9; outline: none;
}
#tier-range::-webkit-slider-thumb {
  -webkit-appearance: none; appearance: none;
  width: 18px; height: 18px; border-radius: 50%;
  background: #2a78d6; border: 2px solid #fcfcfb;
  box-shadow: 0 0 0 1px rgba(11,11,11,0.10); cursor: pointer;
}
#tier-range::-moz-range-thumb {
  width: 18px; height: 18px; border-radius: 50%;
  background: #2a78d6; border: 2px solid #fcfcfb;
  box-shadow: 0 0 0 1px rgba(11,11,11,0.10); cursor: pointer;
}
#tier-slider-wrap .tier-ticks {
  display: flex; justify-content: space-between;
  font-size: 0.8em; color: #52514e; margin-top: 0.4em;
}
</style>

<div id="tier-slider-wrap">
  <div class="tier-readout">request_memory: <span id="tier-readout-value">500MB</span></div>
  <input type="range" id="tier-range" min="0" max="7" step="1" value="0">
  <div class="tier-ticks">
```{r slider-legend, results='asis'}
cat(paste0("<span>", tiers, "</span>", collapse = "\n"))
```
  </div>
</div>

<script>
(function() {
  var tierNames = ["500MB","1GB","2GB","4GB","8GB","16GB","32GB","64GB"];
  var N_TIERS = 8, N_RUNS = 3;

  function plotReady(id) {
    var el = document.getElementById(id);
    return (el && el.data && window.Plotly) ? el : null;
  }

  function apply(idx) {
    var readout = document.getElementById("tier-readout-value");
    if (readout) readout.textContent = tierNames[idx];

    // Overview: enlarge + recolor the selected tier's point.
    var overview = plotReady("overview-plot");
    if (overview) {
      var sizes  = [], colors = [];
      for (var i = 0; i < N_TIERS; i++) {
        sizes.push(i === idx ? 16 : 8);
        colors.push(i === idx ? "#2a78d6" : "#c3c2b7");
      }
      Plotly.restyle(overview, { "marker.size": [sizes], "marker.color": [colors] }, [0]);
    }

    // Throughput: traces are ordered tier 0..7, 3 runs each.
    var throughput = plotReady("throughput-plot");
    if (throughput) {
      var visT = [];
      for (var t = 0; t < N_TIERS * N_RUNS; t++) {
        visT.push(Math.floor(t / N_RUNS) === idx);
      }
      Plotly.restyle(throughput, { visible: visT });
    }

    // Latency: traces 0..7 = turnaround boxes, 8..15 = queue-wait boxes.
    var latency = plotReady("latency-plot");
    if (latency) {
      var visL = [];
      for (var b = 0; b < 2 * N_TIERS; b++) {
        visL.push(b % N_TIERS === idx);
      }
      Plotly.restyle(latency, { visible: visL });
    }
  }

  function init() {
    var range = document.getElementById("tier-range");
    if (!range) return;
    range.addEventListener("input", function() { apply(+range.value); });

    // Plots render after DOMContentLoaded; retry until they exist, then sync
    // to the slider's current position (browsers can restore it on reload).
    var tries = 0;
    var timer = setInterval(function() {
      tries++;
      if (plotReady("overview-plot") && plotReady("throughput-plot") &&
          plotReady("latency-plot")) {
        clearInterval(timer);
        apply(+range.value);
      } else if (tries > 100) {
        clearInterval(timer);
      }
    }, 100);
  }

  if (document.readyState === "loading") {
    document.addEventListener("DOMContentLoaded", init);
  } else {
    init();
  }
})();
</script>


## Where this tier sits in the overall trend

Every tier's median total completion time, for context — the highlighted point
tracks the slider.

```{r overview-plot, fig.height=4}
init_sizes  <- c(16, rep(8, n_tiers - 1))
init_colors <- c("#2a78d6", rep("#c3c2b7", n_tiers - 1))

ov <- plot_ly() %>%
  add_trace(
    data = summary_df, x = ~mb, y = ~median_total_time_s,
    type = "scatter", mode = "lines+markers",
    line = list(color = "#c3c2b7", width = 2),
    marker = list(color = init_colors, size = init_sizes,
                  line = list(color = "#fcfcfb", width = 2)),
    hoverinfo = "text",
    text = ~paste0(tier, ": ", round(median_total_time_s), "s median total time"),
    showlegend = FALSE
  ) %>%
  layout(
    xaxis = list(title = "request_memory", type = "log",
                 tickvals = unname(mb_map), ticktext = names(mb_map)),
    yaxis = list(title = "Median time for all 1,000 jobs to finish (s)"),
    margin = list(t = 10)
  )
ov$elementId <- "overview-plot"
ov
```

## Throughput for the selected tier

Cumulative jobs completed vs. time since cluster submit, for each of the 3
runs at the selected `request_memory`.

```{r throughput-plot, fig.height=5}
p <- plot_ly()
for (ti in seq_len(n_tiers) - 1) {
  for (r in seq_len(n_runs)) {
    d <- long_df %>% filter(tier_idx == ti, run_num == r)
    p <- add_trace(
      p, x = d$turnaround_s, y = d$cum_jobs,
      type = "scatter", mode = "lines",
      line = list(width = 2, color = run_colors[r]),
      name = paste("run", r),
      visible = (ti == 0),
      hoverinfo = "text",
      text = paste0(d$tier, " run ", r, ": ", round(d$turnaround_s, 1),
                    "s — ", d$cum_jobs, " jobs done")
    )
  }
}
p <- p %>%
  layout(
    xaxis = list(title = "Time since cluster submit (s)"),
    yaxis = list(title = "Cumulative jobs completed", range = c(0, 1000)),
    legend = list(title = list(text = "run")),
    margin = list(t = 10)
  )
p$elementId <- "throughput-plot"
p
```

## Per-job latency for the selected tier

Turnaround (submit → termination) and queue wait (submit → first execution),
pooled across the 3 runs at the selected `request_memory` — quartiles
recompute as you move the slider.

```{r latency-plot, fig.height=4.5}
box_style <- list(fillcolor = "rgba(42,120,214,0.15)",
                  line = list(color = "#2a78d6"))

p_turn <- plot_ly()
for (ti in seq_len(n_tiers) - 1) {
  d <- long_df %>% filter(tier_idx == ti)
  p_turn <- add_trace(
    p_turn, y = d$turnaround_s, type = "box", boxpoints = FALSE,
    name = "Turnaround (s)", visible = (ti == 0), showlegend = FALSE,
    fillcolor = box_style$fillcolor, line = box_style$line
  )
}

p_wait <- plot_ly()
for (ti in seq_len(n_tiers) - 1) {
  d <- long_df %>% filter(tier_idx == ti)
  p_wait <- add_trace(
    p_wait, y = d$queue_wait_s, type = "box", boxpoints = FALSE,
    name = "Queue wait (s)", visible = (ti == 0), showlegend = FALSE,
    fillcolor = box_style$fillcolor, line = box_style$line
  )
}

lat <- subplot(p_turn, p_wait, nrows = 1, titleY = TRUE, margin = 0.06) %>%
  layout(margin = list(t = 10))
lat$elementId <- "latency-plot"
lat
```
