---
title: "Memory Request Simulator"
author: "Snikitha Siddavatam"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
subtitle: "How request_memory Changes Job Throughput"
output:
  html_document:
    toc: false
    theme: flatly
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(purrr)
library(plotly)
library(crosstalk)
```

Drag the slider to pick a `request_memory` value and watch how job throughput
for that memory tier compares to the rest. All data below is real: 1,000
HTCondor jobs (S = 10,000 samples each), submitted 3 times at each of 8 memory
requests from 500 MB to 64 GB, with `mc_pi.py` otherwise unchanged across runs.

```{r load-data}
tiers  <- c("500MB", "1GB", "2GB", "4GB", "8GB", "16GB", "32GB", "64GB")
mb_map <- c("500MB" = 500, "1GB" = 1024, "2GB" = 2048, "4GB" = 4096,
            "8GB" = 8192, "16GB" = 16384, "32GB" = 32768, "64GB" = 65536)

read_tier <- function(tier, tier_idx) {
  base <- file.path("memory", paste0("mc_runs_1000_mem_", tier))
  run_dirs <- list.dirs(base, recursive = FALSE)
  run_dirs <- run_dirs[grepl("^run_", basename(run_dirs))]
  purrr::map_dfr(run_dirs, function(rd) {
    f <- file.path(rd, "results.csv")
    if (!file.exists(f)) return(NULL)
    df <- read.csv(f)
    df$run <- basename(rd)
    df
  }) %>%
    mutate(mb = mb_map[[tier]], tier = tier, tier_idx = tier_idx)
}

long_df <- purrr::imap_dfr(tiers, ~ read_tier(.x, .y - 1)) %>%
  group_by(tier) %>%
  mutate(run_label = paste("run", dense_rank(run))) %>%
  ungroup()

summary_df <- long_df %>%
  group_by(tier, tier_idx, mb) %>%
  summarise(
    median_turnaround_s  = median(turnaround_s, na.rm = TRUE),
    p90_turnaround_s     = quantile(turnaround_s, 0.9, na.rm = TRUE),
    median_queue_wait_s  = median(queue_wait_s, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    long_df %>%
      group_by(tier, run) %>%
      summarise(total_time_s = max(turnaround_s, na.rm = TRUE), .groups = "drop") %>%
      group_by(tier) %>%
      summarise(median_total_time_s = median(total_time_s), .groups = "drop"),
    by = "tier"
  ) %>%
  arrange(mb)

long_shared <- SharedData$new(long_df, key = ~tier_idx, group = "mem")
```

## Pick a memory request

<style>
#tier-slider-wrap { max-width: 720px; margin: 1.2em 0 1.6em; }
#tier-slider-wrap .tier-readout {
  font-size: 1.15em; font-weight: 600; color: #0b0b0b;
  margin-bottom: 0.4em;
}
#tier-slider-wrap .tier-readout span { color: #2a78d6; }
#tier-range {
  width: 100%; -webkit-appearance: none; appearance: none;
  height: 4px; border-radius: 2px; background: #e1e0d9; outline: none;
}
#tier-range::-webkit-slider-thumb {
  -webkit-appearance: none; appearance: none;
  width: 18px; height: 18px; border-radius: 50%;
  background: #2a78d6; border: 2px solid #fcfcfb;
  box-shadow: 0 0 0 1px rgba(11,11,11,0.10); cursor: pointer;
}
#tier-range::-moz-range-thumb {
  width: 18px; height: 18px; border-radius: 50%;
  background: #2a78d6; border: 2px solid #fcfcfb;
  box-shadow: 0 0 0 1px rgba(11,11,11,0.10); cursor: pointer;
}
#tier-slider-wrap .tier-ticks {
  display: flex; justify-content: space-between;
  font-size: 0.8em; color: #52514e; margin-top: 0.4em;
}
</style>

<div id="tier-slider-wrap">
  <div class="tier-readout">request_memory: <span id="tier-readout-value">500MB</span></div>
  <input type="range" id="tier-range" min="0" max="7" step="1" value="0">
  <div class="tier-ticks">
```{r slider-legend, results='asis'}
cat(paste0("<span>", tiers, "</span>", collapse = "\n"))
```
  </div>
</div>

<script>
document.addEventListener("DOMContentLoaded", function() {
  var tierNames = ["500MB","1GB","2GB","4GB","8GB","16GB","32GB","64GB"];
  var range = document.getElementById("tier-range");
  var readout = document.getElementById("tier-readout-value");
  var handle = new crosstalk.FilterHandle("mem");

  function apply(idx) {
    readout.textContent = tierNames[idx];
    handle.set([String(idx)]);

    var overview = document.getElementById("overview-plot");
    if (overview && window.Plotly) {
      var sizes  = tierNames.map(function(_, i) { return i === idx ? 16 : 8; });
      var colors = tierNames.map(function(_, i) { return i === idx ? "#2a78d6" : "#c3c2b7"; });
      Plotly.restyle(overview, { "marker.size": [sizes], "marker.color": [colors] }, [0]);
    }
  }

  range.addEventListener("input", function() { apply(+range.value); });
  apply(+range.value);
});
</script>


## Where this tier sits in the overall trend

Every tier's median total completion time, for context — the highlighted point
tracks the slider.

```{r overview-plot, fig.height=4}
plot_ly(elementId = "overview-plot") %>%
  add_trace(
    data = summary_df, x = ~mb, y = ~median_total_time_s,
    type = "scatter", mode = "lines+markers",
    line = list(color = "#c3c2b7", width = 2),
    marker = list(color = rep("#c3c2b7", nrow(summary_df)),
                  size = rep(8, nrow(summary_df)),
                  line = list(color = "#fcfcfb", width = 2)),
    hoverinfo = "text",
    text = ~paste0(tier, ": ", round(median_total_time_s), "s median total time"),
    showlegend = FALSE
  ) %>%
  layout(
    xaxis = list(title = "request_memory", type = "log",
                 tickvals = unname(mb_map), ticktext = names(mb_map)),
    yaxis = list(title = "Median time for all 1,000 jobs to finish (s)"),
    margin = list(t = 10)
  )
```

## Throughput for the selected tier

Cumulative jobs completed vs. time since cluster submit, for each of the 3
runs at the selected `request_memory`.

```{r throughput-plot, fig.height=5}
plot_ly(
  long_shared, x = ~turnaround_s, y = ~j, color = ~run_label,
  colors = c("#9ec5f4", "#3987e5", "#0d366b"),
  type = "scatter", mode = "lines", line = list(width = 2),
  hoverinfo = "text",
  text = ~paste0(tier, " ", run_label, ": ", round(turnaround_s, 1), "s — ", j, " jobs done")
) %>%
  layout(
    xaxis = list(title = "Time since cluster submit (s)"),
    yaxis = list(title = "Cumulative jobs completed", range = c(0, 1000)),
    legend = list(title = list(text = "run")),
    margin = list(t = 10)
  )
```

## Per-job latency for the selected tier

Turnaround (submit → termination) and queue wait (submit → first execution),
pooled across the 3 runs at the selected `request_memory` — quartiles
recompute live as you move the slider.

```{r latency-plot, fig.height=4.5}
p_turn <- plot_ly(
  long_shared, y = ~turnaround_s, type = "box", boxpoints = FALSE,
  name = "Turnaround (s)",
  fillcolor = "rgba(42,120,214,0.15)", line = list(color = "#2a78d6")
)
p_wait <- plot_ly(
  long_shared, y = ~queue_wait_s, type = "box", boxpoints = FALSE,
  name = "Queue wait (s)",
  fillcolor = "rgba(42,120,214,0.15)", line = list(color = "#2a78d6")
)
subplot(p_turn, p_wait, nrows = 1, titleY = TRUE, margin = 0.06) %>%
  layout(margin = list(t = 10))
```
